---
title: "AIC, BIC, CP"
author: "Justin Feathers"
date: '2022-11-19'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE)
```

# Reads in libraries and `effervescence.csv` dataset
```{r}
library(tidyverse)
library(broom)
library(caret)
df_eff <- read_csv('effervescence.csv', col_types = 'fffnnn')
```

# Full model
* RMSE = 1.075
* AIC = 155.3374
* BIC = 179.663
```{r}
lm_eff <- lm(Time ~ Brand * Temp * Stirred, data = df_eff)
summary(lm_eff)
glance(lm_eff)
```

# Stirred as block effect
* RMSE = 1.319
* AIC = 171.1984
* BIC = 186.168
```{r}
lm_block_eff <- lm(Time ~ Brand * Temp + Stirred, data = df_eff)
summary(lm_block_eff)
glance(lm_block_eff)
```

# Covariate order with 3 factor interaction
* RMSE = 1.087
* AIC = 157.0557
* BIC = 183.2525
```{r}
lm_three_order_eff <- lm(Time ~ Brand * Temp*Stirred + Order, data = df_eff)
summary(lm_three_order_eff)
glance(lm_three_order_eff)
```

# Covariate order with stirred as block effect without interaction
* RMSE = 1.303
* AIC = 170.872
* BIC = 187.7129
```{r}
lm_block_order_eff <- lm(Time ~ Brand * Temp + Stirred + Order, data = df_eff)
summary(lm_block_order_eff)
glance(lm_block_order_eff)
```

# For SAS Appendix models:  
## Random Temp, Random Brand  
* RMSE = 1.83
* AIC = 224.9
* BIC = 221.3

## Fixed Temp, Random Brand  
* RMSE = 1.83
* AIC = 208.3
* BIC = 204.4

## Random Temp, Fixed Brand  
* RMSE = 1.83
* AIC = 216.8
* BIC = 214.1 

