---
title: "Analysis and Results"
author: ""
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis and Results

### Order as a Model Covariate  
We next consider the run order variable Order as a covariate.  We first considered the relationship between Order and the response Time.  
```{r Time and Order Plot, message=FALSE, warning=FALSE}
#using Halid's read_csv code to keep data frame consistent
library(tidyverse)
df_eff <- read_csv('effervescence.csv', col_types = 'fffnnn')


##get correlation to add to plot
correlation <- cor(df_eff$Time,df_eff$Order)

##construct scatter plot of Time by Order with fitted SLR line
## add correlation result to this plot
gOrderTime <- ggplot(df_eff,aes(x=Order,y=Time))
gOrderTime + geom_point() +geom_smooth(method=lm,col="Red",se = F) + 
  geom_text(x=35,y=63,size=6, label = paste0("Correlation = ",round(correlation, 2))) + 
  labs(title = "Scatter Plot of Time by Order with Fitted \nLinear=Red and Quadratic=Blue Regression Lines") +  
  geom_smooth(method=lm,formula = y~poly(x,2),col="Blue",se=F)
```

The preceding scatter plot does shows only a weak positive linear relationship between Order and Time with a small correlation=0.2.  However, the plot does show a plausible quadratic relationship between Order and Time.  
```{r}
##Create new Order^2 variable
df_eff$Order2<-df_eff$Order^2

#Fit quadratic model with order and order^2
slrOrderQ<-lm(Time~Order+ Order2,data = df_eff)
summary(slrOrderQ)
```
A fitted quadratic regression model was significant with overall overall F test p-value=0.013 and all coefficients having p-values less than .05.  Thus, we decided to include both Order and Order^2 as additive covariates in the following full three factor interaction model.  

```{r message=FALSE, warning=FALSE}
#added covariates Order to model with 3 factor interaction
aov_three_order_eff <- aov(lm_three_order_eff <- lm(Time ~ Brand*Temp*Stirred + Order+ Order2, data = df_eff))
summary(lm_three_order_eff)
library(car)
Anova(aov_three_order_eff, type=3) # type 3 SS
```




